% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Tal Berenstein}{November 13, 1990}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:tal.berenstein@pm.me}{tal.berenstein\mbox{}@\mbox{}pm.me}\sbull
\textsmaller{+}46 765535845\sbull
\href{https://github.com/talberenstein}{github.com/talberenstein}\sbull
\href{https://linkedin.com/in/tali-berenstein-torres-94055726b/}{linkedin.com/tal-berenstein}
\\
Godemansgatan 9A,
41706\thinspace {\large \sc }\sbull
Göteborg\sbull
Sweden

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Entrepreneurial geek with roots in the open-source movement. Passionately enabling software-related teams to deliver. Creating/\ improving processes to achieve the best possible result. Adaptive to both individuals and multicultural groups. Right now working as a Functional Team Leader at Volvo Group.}
\\
\\
At the age of six (1996), I got my first laptop in a humble house in \emph{Valparaíso, Chile}.  An old one with \acr{Windows 3.1} on a \acr{IBM I-Series} laptop. Spending hours playing with the MS-DOS shell back in those years, my passion for coding started. 11 years later (2007) I attended my first conference on an emerging new product, the new iPhone 3G, at the \emph{Universidad Diego Portales} in \emph{Santiago}.

After that conference I decided to study at the same University, motivated by the group of teachers and exposers at that conference. I taught myself a variety of skills, including system administration and programming (Java, Javascript, Ruby \& \CPP), along with the theoretical knowledge given by the program. In 2013 I was invited to a new Start-up with offices in Brazil. It was my first approach to SCRUM methodology.

Extensively traveled in Oceania and Asia when I started to feel I needed to also achieve a skill that I did not know I had: natural languages. I taught myself Portuguese, English, and currently learning Swedish. All those years I  worked as a freelancer for different projects and different groups of people and cultures. Currently leading a group of Front-end developers and designers for Volvo Group Connected Solutions and participating in a 6-month course of {\href{https://www.globalleadership.com/en/}{\acr{Global Functional Leaders}}} in Gothenburg, Sweden.



\end{multicols}


\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection
  {\href{https://www.volvogroup.com/en/about-us/organization/other-entities/volvo-group-connected-solutions.html}{\acr{Volvo Group Connected Solutions}}}
  {\textsc{Gothenburg, Sweden}} {%
  \headedsubsection
    { \acr{Senior Front-end Software Engineer} }
    {May \apo24 -- present}
    {\bodytext{Mentored and led a team of front-end engineers, driving the development of high-quality, responsive web applications while fostering a culture of continuous learning and technical excellence.
    
Developed and delivered technical training sessions, improving team proficiency in modern front-end frameworks, coding standards, and best practices, resulting in a 20\% increase in code efficiency and a reduction in bug reports.

Provided strategic guidance and hands-on coaching to junior engineers, enhancing their problem-solving skills and enabling them to take on more complex tasks, thereby accelerating project timelines and improving overall team performance.

    }}
}

\headedsection
  {\href{https://www.volvogroup.com/en/about-us/organization/other-entities/volvo-group-connected-solutions.html}{\acr{Volvo Group Connected Solutions}}}
  {\textsc{Gothenburg, Sweden}} {%
  \headedsubsection
    { \acr{Domain/Technical Team Leader} }
    {Feb \apo23 -- present }
    {\bodytext{As a Technical Leader for the Frontend team, I play a pivotal role in guiding our skilled team of frontend developers. My responsibilities span both technical expertise and leadership, ensuring the successful delivery of rich, responsive web applications and progressive web apps (PWAs).
    
    \sbull Insights of my daily job: Leading the Technical Direction, Product Design and Feature Development, Code Quality and Optimization, Mentoring and Professional Growth, Business Alignment.
    }}
}

\headedsection
  {\href{https://www.volvogroup.com/en/about-us/organization/other-entities/volvo-group-connected-solutions.html}{\acr{Volvo Group Connected Solutions}}}
  {\textsc{Gothenburg, Sweden}} {%
  \headedsubsection
    { \acr{Professional Software Engineer} }
    {Feb \apo21 -- present}
    {\bodytext{Developing within an agile team a portal with technical tools and applications for a wide group of users to enable in-depth troubleshooting and data analysis across a complete stack of micro-services for connected solutions.
Developing, deploying, and operating a frontend stack for these new tools and applications according to development standards and clean architecture.

Source code management systems such as Gerrit GIT and GitHub,  micro-service architecture e.g. AWS cloud services, event-driven systems and web socket programming, CLEAN architecture, and DRY programming.

\sbull Keywords: React, SCRUM, Javascript, GIT, CI/CD, Confluence, AWS
}}
}

\headedsection
  {\href{http://talberenstein.github.io}{\acr{Tal Berentein - Freelance.}}}
  {\textsc{Melbourne, Australia}} {%
  \headedsubsection
    {Freelance \acr{Full-Stack} Developer}
    {Oct \apo17 -- Jan\apo21t}
    {\bodytext{Provides services related to software development such as:\@ coaching, audits, process improvement, web/cloud architecture and stack strategies.  (Mostly but not only: NodeJS, GraphQL, React (Js and Native), Javascript, HTML5 and CSS, PHP). Also worked with SQL and NoSQL databases.
  \\ Clients:\@ \href{http://www.happycamperpizza.com.au}{HappyCamperPizza.com.au}, \href{https://delightchile.cl}{DelightChile.cl} \& \href{https://www.orakelforlag.se}{OrakelFörlag.se}.}}
}

\headedsection
  {\href{http://www.gestsol.cl}{Gestsol}}
  {\textsc{Santiago, Chile}} {%
  \headedsubsection
    {Front-end Developer}
    {Apr \apo15-- Oct \apo16}
    {\bodytext{Front-end mobile and web developer using technologies such as Ionic, Angular 1.x, CoffeeScript and Ruby on Rails 5.0. Mobile application similar to Netflix, fetching data from PHP endpoints to show in a video player developed by the team. Web Application GPS Real-Time application on CoffeeScript and Ruby on Rails fetching data and creating models from/to API developed in Elixir Erlang.}}
}


\vspace{-0.2em}
\begin{center}
  \emph{\small Please refer to \href{http://www.linkedin.com/in/tal-berenstein}{Tal's LinkedIn profile} for a more complete list of work experience along with recommendations.}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{https://www.globalleadership.com/en/l}{Global Functional Leaders}}
  {\textsc{Gothenburg, Sweden}} {%
  \headedsubsection
    {BSc in Computer Science \textnormal{~(\acr{CS}~\,\&\,Telecomunications)}}
    {Sept '23 -- March '24}
    
}

\headedsection
  {\href{http://www.udp.cl}{Diego Portales University}}
  {\textsc{Santiago, Chile}} {%
  \headedsubsection
    {BSc in Computer Science \textnormal{~(\acr{CS}~\,\&\,Telecomunications)}}
    {2009 -- 2013}
    
}


\spacedhrule{0.5em}{-0.4em}

\roottitle{Another Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Teaching experience:}
  {  Currently, I am teaching a small group of junior developers about React, Typescript, and CLEAN architecture, so they can get their first job in this passionate field. }

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {Spanish \emph{(mother tongue)}, English \emph{(full professional proficiency)}, Swedish \emph{(working proficiency)} and Portuguese \emph{(limited working proficiency)} }


\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {Art, Buddhism, Chess, Cryptography, Functional programming, History, Music (special love for Argentinian Tango), Open water swimming, Philosophy, Poetry, Startups, Swimming, Travel, Typography (e.g. \LaTeX), \acr{UX}-design, Vegetarian cuisine, \acr{VRP} (Vehicle Routing Problem)}


\end{document}
